---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
seabird_count <- read_csv("../task_3/clean_data/seabird_count.csv")
```
# 1.3.2 Analysis questions

# For each question where we ask for bird names, give the bird’s common name, scientific name and species abbreviation.

# 1. Which bird had the most individual sightings?

```{r}
seabird_count %>% 
  select(species_common_name, species_scientific_name, species_abbreviation) %>% count(species_common_name, species_scientific_name, species_abbreviation) %>% 
  arrange(desc(n))
```
# 2.Which bird had the highest total count?
```{r}
seabird_count %>% 
  select(species_common_name, species_scientific_name, species_abbreviation, count) %>% 
  group_by(species_common_name) %>% 
  count(count) %>% 
  summarise(total = sum(count)) %>% 
  arrange(desc(total))
```
# 3. Which bird had the highest total count above a latitude of -30?

```{r}
seabird_count %>% 
   select(species_common_name, species_scientific_name, species_abbreviation, count, lat) %>% 
  filter(lat > -30) %>% 
  group_by(species_common_name) %>% 
  count(count) %>% 
  summarise(total = sum(count)) %>% 
  arrange(desc(total))
```

# 4. How many different types of birds were only ever seen in groups of 1?

```{r}
seabird_count %>% 
  select(species_common_name, count) %>% 
  filter(count == 1) %>% 
  distinct(species_common_name) %>% 
  count(species_common_name) %>% 
  summarise(sum(n))
```

# 5. How many penguins were seen? 

