---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```

```{r}
boing_boing <- read_csv("../task_4/clean_data/boing_boing_full.csv")
```
# 1.4.2 Analysis questions

#1. What is the total number of candy ratings given across the three years. (Number of candy ratings, not the number of raters. Don’t count missing values)

```{r}
boing_boing %>% 
  filter(!is.na(rating)) %>% 
  summarise(candy = n())
```


#2. What was the average age of people who are going out trick or treating?

```{r}
boing_boing %>% 
  filter(trick_or_treating == "Yes") %>% 
  mutate(mean_age = mean(age, na.rm = TRUE),
         .after = age)
```


#3. What was the average age of people who are not going trick or treating?

```{r}
boing_boing %>% 
  filter(trick_or_treating == "No") %>% 
  mutate(mean_age = mean(age, na.rm = TRUE),
         .after = age)
```

#4.For each of joy, despair and meh, which candy bar received the most of these ratings? 

# Joy!

```{r}
boing_boing %>% 
  select(candy, rating) %>% 
  filter(rating == "JOY") %>% 
  group_by(candy) %>% 
  count(rating) %>% 
  arrange(desc(n)) %>% 
  head(5)
 
```
# Despair

```{r}
boing_boing %>% 
  select(candy, rating) %>% 
  filter(rating =="DESPAIR") %>% 
  group_by(candy) %>% 
  count(rating) %>% 
  arrange(desc(n)) %>% 
  head(5)
```

#MEH

```{r}
boing_boing %>% 
  select(candy, rating) %>% 
  filter(rating == "MEH") %>% 
  group_by(candy) %>% 
  count(rating) %>% 
  arrange(desc(n)) %>% 
  head(5)
```

#5. How many people rated Starburst as despair?

```{r}
boing_boing %>% 
  select(candy, rating) %>% 
  filter(candy == "starburst", rating == "DESPAIR") %>% 
  count(candy)
```
# For the next three questions, count despair as -1, joy as +1, and meh as 0.

```{r}
boing_boing_score <- boing_boing %>% 
  mutate(score = case_when(
    rating == "JOY" ~ 1,
    rating == "MEH" ~ 0,
    rating == "DESPAIR" ~ -1
  ))
```

#6. What was the most popular candy bar by this rating system for each gender in the dataset ?

```{r}
boing_boing_score %>% 
  group_by(gender, candy) %>% 
  summarise(mean_score = mean(score, na.rm = TRUE)) %>% 
  slice_max(mean_score)
```

#7. What was the most popular candy bar in each year?
```{r}
boing_boing_score %>% 
  group_by(year, candy) %>% 
  summarise(mean_score = mean(score, na.rm = TRUE)) %>% 
  slice_max(mean_score)
```
#8. What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?
```{r}
boing_boing_score %>% 
  group_by(country, candy) %>% 
  summarise(mean_score = mean(score, na.rm = TRUE)) %>% 
  slice_max(mean_score)
```

