---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
decathlon <- read_csv("../clean_data/decathlon_finish.csv")
```

# 1.1.2 Analysis questions

# 1) Who had the longest long jump seen in the data?

```{r}
decathlon %>% 
  select(name, long_jump) %>% 
  arrange(desc(long_jump)) %>% 
  slice(1)
```

# 2. What was the average 100m time in each competition?

# Olympic G

```{r}
decathlon %>% 
  filter(competition == "OlympicG") %>% 
  mutate(mean_100m = mean(x100m),
         .after = x100m)
```

# Decastar 

```{r}
decathlon %>% 
  filter(competition == "Decastar") %>% 
  mutate(mean_100m = mean(x100m),
         .after = x100m)
```

# 3.Who had the highest total points across both competitions?

```{r}
decathlon %>% 
  group_by(name) %>% 
  mutate(points_total = sum(points)) %>% 
  summarise (points_total) %>% 
  arrange (desc(points_total)) %>% 
  head(1)
```

# 4.What was the shot-put scores for the top three competitors in each competition?

```{r}
decathlon %>% 
  select(name, shot_put, points, competition) %>% 
  filter(competition == "OlympicG") %>% 
  arrange(desc(points)) %>% 
  head(3)
```

```{r}
decathlon %>% 
  select(name, shot_put, points, competition) %>% 
  filter(competition == "Decastar") %>% 
  arrange(desc(points)) %>% 
  head(3)
```

# 5.What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

# Above 50 seconds

```{r}
decathlon %>% 
  filter (x400m >= "50") %>% 
  mutate(mean_points = mean(points),
         .after = points)
```

# Below 50 seconds
```{r}
decathlon %>% 
  filter (x400m < "50") %>% 
  mutate(mean_points = mean(points),
         .after = points)
```

